 
---
title: "ACAQ Visualizer"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F)
```

# ACAQ: a Fiji and R toolkit targeted for automated confrontation assay quantification

Zoltan Cseresnyes (1,+), Naim Al-Zaben (1,2,+), Mohamed I. Abdelwahab Hassan (2,3,4), Ruman
Gerst (1,2), Kerstin Voigt (3), Marc Thilo Figge (1,2,*)

(1) Applied Systems Biology, Leibniz Institute for Natural Product Research and Infection Biology –
Hans Knöll Institute, Jena, Germany
(2) Faculty of Biological Sciences, Friedrich Schiller University Jena, Jena, Germany
(3) Jena Microbial Resource Collection, Leibniz Institute for Natural Product Research and Infection
Biology – Hans Knöll Institute, Jena, Germany
(4) Pests and Plant Protection Department, National Research Centre, Giza, Egypt
(+) These authors contributed equally to this work.
(*) Correspondence should be addressed to MTF: thilo.figge@leibniz-hki.de.

Host-pathogen interactions are ideally studied by imaging confrontation assays, where interacting
cell types are monitored during and/or after their interaction. The resulting images are quantified
via automated segmentation and classification algorithms, which help to unravel biological
functions from host-pathogen interactions. Here we describe a modular and easily extendable
segmentation and analysis framework designed both for fluorescently labeled and unlabeled cells
participating in such interactions. Acquiring images of unlabeled biological samples has multiple
advantages: it minimizes the side effects that fluorescence labeling may have on biological
functions, and it saves the time and expense spent on fluorescence labeling. Our new high-
throughput confrontation assay-analysis and -visualisation open-source toolkit, algorithm for
confrontation assay quantification (ACAQ), is a Fiji macro extended by R. It consists of two parts:
ACAQ Analyzer and ACAQ Visualizer. The former is designed to analyze cells in two-dimensional
microscopy images, using either fluorescence labeling or transmitted light bright-field microscopy.
In the absence of labeling, Hessian filter-based segmentation is used, which is able to distinguish
between various types of cells that differ in size. The ACAQ toolkit computes a collection of
phagocytosis measures and morphological descriptors. The results are summarized and exported
by ACAQ Visualizer, providing immediate feedback to the user.

# Running

To run ACAQ Visualizer, go into the `ACAQ Visualizer` directory.

* If you are on Linux, start a terminal in this folder and run `./run.sh`
* If you are on Windows, run `run.bat`

## Requirements (Linux only)

If you are on Linux, install R version `r sessionInfo()$R.version$version.string` or higher.

## R packages


```{r, results = 'asis'}

library(knitr)
library(rmarkdown)

r.packages <- sessionInfo()$otherPkgs

table <- data.frame(
  Package = sapply(r.packages, function(x) { x$Package }),
  Author = sapply(r.packages, function(x) { if("Author" %in% names(x)) gsub("\n", " ", x$Author) else "" }),
  URL = sapply(r.packages, function(x) { if("URL" %in% names(x)) gsub("\n", " ", x$URL, fixed = T) else "" }),
  "License" = sapply(r.packages, function(x) { gsub("|", ";", x$License, fixed = T) }),
  "Version" = sapply(r.packages, function(x) { x$Version }),
  stringsAsFactors = F,
  check.names = F,
  row.names = NULL
)

kable(table, caption = "Required packages")

```

We provide the source code of each package with ASAQ Visualizer You can find their sources and licenses in `ACAQ_Shiny/packrat/src`.

## Updating this README file

This README file is autogenerated using RMarkdown. Please don't forget to run ACAQ Visualizer once before
rebuilding this README.

**Note:** You cannot use RStudio as RStudio's RMarkdown builder runs in a separate environment!

```
# Run ACAQ Visualizer once
shiny::runApp()
# Cancel with Ctrl + C
# Build the README file
rmarkdown::render("README.Rmd")
```
